Genome-wide changes in expression during inflorescence architecture development

### 2015-08-05 ms.Rmd
SHIT. Typo in DESeq script causing spikelet meristem samples to be treated as rachis meristem. Good one.
mfuzz script

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
output:
  pdf_document:
    fig_caption: yes
    keep_md: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

## Dissections in early stages of inflorescence development
+  **Figure**: laser microdissections

## Transcriptome sequencing of meristem samples
+ Max. 1 paragraph about boring sequencing stats
+ **Table** (or supplementary): # reads, mapping %, rRNA, introns, genes blah blah

>>>>

---
title: "Genome-wide changes in expression during inflorescence architecture development
  in rice"
csl: csl/the-plant-journal.csl
output:
  pdf_document:
    fig_caption: yes
    keep_md: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

## Dissections in early stages of inflorescence development

+  **Figure**: laser microdissections

## Transcriptome sequencing of meristem samples

+ Max. 1 paragraph about boring sequencing stats
+ **Table** (or supplementary): # reads, mapping %, rRNA, introns, genes blah blah
